---
title: "ECON 323 Assignment 1"
output: html_notebook
---

Loading the data
```{r load}
rm(list=ls())

db <- read.csv("census2016.csv", header = TRUE, stringsAsFactors = FALSE)

head(db)
```
The data contains 930421 observations from 5 variables AGEGRP (Age group), CfSize (Census Family Size), ROOMS (No. of rooms in the dwelling), Sex (Gender) and CfInc (Total Income).

Transforming the data 
```{r transform data}
library(plyr)

map <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,88)

val <- c(2,5.5,8,10.5,13,16,18.5,22,27,32,37,42,47,52,57,62,67,72,77,82,88,NA)

db$AGECON <- mapvalues(db$AGEGRP, from = map, to = val)

db$ROOMS[db$ROOMS == 88] <- NA
db$CfSize[db$CfSize == 8] <- NA
db$CFInc[db$CFInc == 88] <- NA
db$Sex[db$Sex == 2] <- 0

db <- subset( db, select = -X )

db2 <-na.omit(db)
```
The data is transformed such as AGECON is created to represent age as a continuous variable. Any category indicating unknown is converted to NA and removed from the dataset. The dataset used for upcoming part now contains 907308 observations. 

Perform linear regression of rooms on other variables.
```{r reg}
olsreg <- lm(ROOMS ~ Sex + AGECON + CfSize + CFInc, data = db2)
summary(olsreg)
```
```{r}
olsreg1 <- lm(ROOMS ~ CfSize + CFInc, data = db2)
summary(olsreg)
```

2-sided T-test for coeff Sex = -.5; 
B0 = -.5 (null hypo)
B1 =/= .5 (alt hypo )
```{r}

beta_reg <- coef(olsreg)

beta_age <- beta_reg [3]

se_age <- sqrt(vcov(olsreg)[3,3])

t_age <- (beta_age + 0.5)/se_age
t_age

df_olsreg <- olsreg$df
df_olsreg

qt(0.975,df_olsreg)
```

Heteroskedasticity determination using BP test 
```{r}
library(lmtest)
bptest(olsreg)
```
